A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-11-05 manuscript.Rmd
rename to manuscript close #58

keywords          : "keywords"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('rr-flow.Rmd')), error=function(err) 'NA')`"

@@

all: rr-flow.pdf

@@

rr-flow.pdf: rr-flow.Rmd reproducible-research.bib
	$(run) Rscript -e 'rmarkdown::render("$(current_dir)/$<")'
```

>>>>

keywords          : "keywords"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')), error=function(err) 'NA')`"

@@

all: manuscript.pdf

@@

manuscript.pdf: manuscript.Rmd reproducible-research.bib
	$(run) Rscript -e 'rmarkdown::render("$(current_dir)/$<")'
```
